\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{longtable}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
\lstset{style=mystyle}

\usepackage[left=1in,right=1in,top=1in,bottom=1.5in]{geometry}
\author{Jacob H. Nie}
\title{A Lexicographic Analysis of Similarities in the Pauline Epistles}
\begin{document}
\maketitle
\tableofcontents

\break


Disclaimer 1: This was mostly a personal project to practice my programming skills.  I was surprised by the results, especially since I did not need to optimize anything to attain them.  Real algorithms to analyze authorship are (probably) more complex and reliable, so this shouldn't be considered a substitute for real scholarship.  

Disclaimer 2: Any information about current scholarly consensus should be taken with a grain of salt.  First of all, most outside information in this paper came from Wikipedia.  At the very best, it's a bad research practice and at the very worst, the information is wrong.  Also, please note that both Wikipedia and modern critical analysis are skewed against conservative religious thought due to the general overrepresentation of progressive scholarship in universities.  Modern scholars are extremely quick to reject claims to authorship on the basis of occasionally minute details.  

Disclaimer 3: For the Christian, rejecting the teachings of certain books because they are pseudepigraphic is dangerous business.  Many times, they are considered pseudepigraphic largely in part due to the presence of ``inconvenient'' doctrines (misogyny is the biggest culprit) or simply because it seems different.  

With that said, let's dive right in.  
\section{Introduction}
New Testament authorship is a tricky subject.  Most books have claims to authorship (in other words, the author directly writes, ``It is me, Jacob, who wrote this''), but other books have either no claims, or only indirect claims (like in John), to authorship.  And even among the books with claims to authorship, many modern scholars now dispute these claims, suggesting that these books were actually written by a later person pretending to be the claimed author.  (The scholarly term is ``pseudepigraphical.'')  

Here's the general consensus among modern day scholars.

\subsection{Modern Scholarship}

We can split up the New Testament into five sections: the four Gospels (each giving an account of the ministry, crucifixion, and resurrection of Christ), the Book of Acts (a history of the early church following the resurrection), the Pauline Epistles (letters written by Paul to churches and specific people), the Catholic Epistles (letters written to the ``catholic'', or general, church not to be confused with the modern day Roman Catholic Church), and the Book of Revelation (a book containing end-time prophecies.)

The Gospels are ascribed to the authors named in the title.  Among the four Gospels, we call the first three (Matthew, Mark, and Luke) the Synoptic Gospels.  The fourth, John, reads somewhat differently from the first three.

The Book of Acts does not claim an author, but most scholars agree that it is written by the same person who wrote Luke (who we think is Luke but very well might not be).  

The Epistles are a complex territory.  Seven letters are considered genuine works by Paul: 1 Thessalonians, Galatians, 1 Corinthians, Philippians, Philemon, 2 Corinthians, and Romans.  Scholars are split on the authenticity of two letters by Paul: Colossians and 2 Thessalonians.  Most scholars believe four letters are ``fakes'' (pseudepigraphic): Ephesians, 1 Timothy, 2 Timothy, and Titus.  Hebrews is anonymous but is usually categorized with the Pauline Epistles, but very few people think it is written by Paul, even in the Church itself.

It is much more difficult to say something concrete about the Catholic Epistles for two reasons.  One, much less is known about the lives of these authors, unlike Paul, of whom we have a detailed record of his entire Christian life in the book of Acts.  Two, Paul's body of scholarship is much larger and much easier to compare across.  James is written by somebody named James, but there are a couple of James's.  The opinion is split.  1 Peter is very contested as well.  (Peter was a fisherman, how could he write so well?  But there is evidence for it still.)  2 Peter is generally considered to be written by somebody other than Peter.  1, 2, and 3 John are generally considered to be written by the same person who wrote the Gospel of John (but not necessarily John!).  Finally, the authorship of Jude is disputed.

The Book of Revelation is attributed to John, and traditionally this John has been thought to be the same John that wrote the Gospel of John, but now this is disputed due to significant stylistic differences.  

\subsection{My analysis}

For our analysis, we will only consider the Pauline epistles.  Trying to form any claim about authorship in other books is impossible because there aren't many books written by the same author that can be compared to.  For example, it would be pointless to try to determine whether James wrote James from a purely stylistic analysis: we have no other writings by James to compare it to.  

Why can't we examine the Johannine literature?  Because comparing the books of John and 1, 2, 3 John and Revelation is like comparing apples to oranges.  The books have different purposes and different audiences---any difference in language would not speak much.  Furthermore, the sizes of the Johannine books vary too widely.  Nevertheless, you can try and form your own claims about the authorship of Johannine books by taking a look at the raw data in Appendix B.

So to summarize, the big question is: \emph{Which Pauline Epistles were actually written by Paul?}

\section{Method}
Our method is conceptually simple and only involves looking at the word frequencies in the original Greek.  (No examination of grammatical structures or word combinations.)  Here is the general structure of our method. 

\subsection{Summary} 

First, we determine the frequencies of each Greek word as it appears in each book.  (We use root words.  For example, in English we would consider \emph{run}, \emph{ran}, \emph{running}, and \emph{runs} to be identical.)  

Then, to compare two books, we will calculate the \emph{degree of dissimilarity}.  If one word has a high frequency in the first text but a low frequency in the second text, then this will add significantly to the degree of dissimilarity.  If another word appears equally frequently or infrequently in both texts, then this will add zero to the degree of dissimilarity.  

Note: we will limit ourselves to the most common words (the 10 most common in each book).  Here is why.  We are looking for stylistic differences and not topical differences.  For example, Paul talks about circumcision often in Romans but never in 2 Corinthians.  But that should not discredit the stylistic similarities between the two books!  So we stick to the 10 most common words in each book, which happen to be mostly prepositions, conjunctions, and pronouns.  (Refer to Appendix A for a table of the 20 most common words in each book, along with the frequencies.)

One might think, how could you possibly expect to glean any kind of results simply by looking at the frequencies of the most insignificant words like ``is,'' ``but,'' and ``the''?  The results can be surprising.

\subsection{A bit more detail}

Now I will explain the method in more detail.

Let $\{m_i\}$ be the set of book M's top 10 words.  Let $\{n_i\}$ be the set of book N's top 10 words.  Then let $\{w_i\}$ be the union of $\{m_i\}$ and $\{n_i\}.$  (The size of $\{w_i\}$ is anywhere between 10 and 20.  This skews our final number, but in the right direction.  You'll see.)

Let $f_m(w_i)$ be the frequency of word $w_i$ in book M (occurrences divided by total words).  Let $f_n(w_i)$ be the frequency of word $w_i$ in book N.  Note that it is possible, but unlikely, that word $w_i$ doesn't appear in one of the books.  In that case, we take note of $\{w_i\}$ but omit it from the set.  (We can't do $\ln 0$ as you will see.)

My formula for the degree of dissimilarity, $a$, is:
\begin{equation*}
a = \sum s_i = \sum |\ln f_m(w_i) - \ln f_n(w_i)|.
\end{equation*}
A small $a$ means the two books are similar, a large $a$ means the two books are not similar.  Unfortunately, we can't look at a specific value of $a$ and determine whether this means the books are similar or dissimilar.  We can only look at two pairs of books and determine which pair is more similar.  

Note: I use a logarithm to give proper weight to less common words.  For example, if one word has $f_m(w_i) = 0.15$ and $f_n(w_i) = 0.13$ and another word has $f_m(w_{j}) = 0.02$ and $f_n(w_{j}) = 0.001,$ then the absence of a logarithm would make these two words contribute equally to $a$: $|f_m(w_i) - f_n(w_i)| = |f_m(w_j) - f_n(w_j)|.$  However, it's clear that $w_{j}$ shows the largest, most significant stylistic difference.  The logarithm solves that issue.

\subsection{A clarifying example}
I'll make this in English and not Greek so it's a bit more clear.  And also, instead of the top ten words in each book, we'll take the top three words instead.  And the two books we compare will be: \emph{The Catcher in the Rye} and \emph{The Old Man and the Sea}.  (Data is fake, if that's not clear.)
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\emph{The Catcher in the Rye} & $f_1(w)$ & \emph{The Old Man and the Sea} & $f_2(w)$ \\ \hline \hline
the & 0.15 & the & 0.14 \\ \hline
and & 0.07 & for & 0.06 \\ \hline
is & 0.02 & and & 0.03 \\ \hline
\vdots & \vdots & \vdots & \vdots \\ \hline
for & 0.01 & is & 0.005 \\ \hline
\end{tabular}
\end{center}
Using the same notation as we did above, $\{m_i\} = $ \{the, and, is\}, and $\{n_i\} = $ \{the, for, and\}.  Then $\{w_i\} = $ \{the, and, is, for\} $= \{w_1, w_2, w_3, w_4\}.$  

We calculate: 
\begin{align*}
s_1 = |\ln 0.15 -  \ln 0.14| &= 0.069\\
s_2 = |\ln 0.07 - \ln 0.03| &= 0.847\\
s_3 = |\ln 0.02 - \ln 0.005| &= 1.386 \\
s_4 = |\ln 0.01 - \ln 0.06| &= 1.792\\
\end{align*}
Hence, our degree of dissimilarity is $a = 0.069 + 0.847 + 1.386 + 1.792 = 4.094.$  The word that contributes most, the word that has the largest discrepancy, is ``for''.  

\subsection{Finding similar works in a group of works}
(This section explains what the function \textbf{mostSimilarIn} (Section 3) does.)

Suppose we have five books, (A, B, C, D, and E).  We've calculated the $a$-values for each pair of these five books, and we want to find the three out of the five books that are most similar to one another.  

How do we do this?  We test each possible size 3 subset of the five books (ABC, ABD, ABE, etc) and see which one has the lowest ``total $a$-value.''  In other words, which subset has the lowest sum of all the pairwise $a$-values.  Then, this subset is the subset of books that is most similar to one another.

In the program I wrote, you would call:
\begin{verbatim}
mostSimilarIn([A, B, C, D, E], 3)
>>> ([A, C, D], 5.313151)
\end{verbatim}
where the second number is the average pairwise $a$ value.  (As before, lower means more similar!)

\section{Computer Work}
I used Python 3.  I downloaded a .csv file of the entire Greek New Testament (each line containing one word and its Strong's Number along with morphological tags that I ignored) from \underline{\href{https://github.com/biblicalhumanities/Nestle1904/tree/master/morph}{here}}.  

Next, I split up the .csv file into books.  Each book had a corresponding 1-D array of the words that it contained.  

Following that, I wrote a function that would return, in array form, each unique word along with the frequency with which it occurred in the book, ordered from most common to least common.  I also created a dictionary for each book that would allow me to quickly access the frequency of each word.

Then, I wrote a function (\textbf{compare1}) to return the $a$ value for any two input books, along with the five words that contributed most significantly to $a$ (i.e. the words for which $s_i = |\ln f_m(w_i) - \ln f_n(w_i)|$ was the largest).  

Next, I wrote a function (\textbf{mostSimilarTo}) that would take in an input book and return the $a$ values for it vs. the 26 other books, then ranking which books were most similar and most dissimilar to the input book. (Results in Appendix B)

Finally, I wrote a function (\textbf{mostSimilarIn}) that would take a sublist of $n$ books and return the $k\leq n$ most similar books within that sublist.  The returned subset would be the subset of size $k$ that minimized the sum of all $\binom{k}{2}$ degrees of dissimilarity between all pairs of books within that subset.  Furthermore, the function also returns the average value of $a$ (the degree of dissimilarity) within all book-pairs within the returned subset.  

The complete Python code is found in Appendix C.  

\section{Results}
Please see Appendix A and B for the raw results.  Appendix A lists the top 20 most common words in each book, along with each word's frequency.  Appendix B lists, for each book, the $a$ values for that book and all 26 other books.  

Let's try to see how our data answers our main question.  Of course, we can't expect a clear, definite answer using only the limited analysis provided, but we can get a sense of how consistent our method is with current scholarship.  

\textbf{Which Pauline Epistles were actually written by Paul?}

To answer this question, we will use the function $\textbf{mostSimilarIn},$ which is the same method as explained in Section 2.4.  

We will examine the 13 Pauline Epistles, not including Hebrews.  First, we will look for the two most similar works.  Then, we will look for the three most similar works.  (In other words, out of these 13 books we try every possible combination of three books and see which combination is the most similar to one another.)  Hopefully, by the time we get to the five and six most similar works, a clear ``in-group'' of similar books will begin to take shape.  

Towards the end, when we start looking for the 11 and 12 most similar books, the books that only just begin to appear are going to be the clear odd ones out.

If our developing ``in-group'' of similar books is consistent with what scholarship believes to be authentic Pauline literature, then we can estimate an approximate ranking of which books are ``most Pauline'' and ``least Pauline.''

The results are listed in the table below.  (For your convenience, I have bolded the books that ``have just appeared'', i.e. the books that are not in the row directly above it.)

\begin{center}
\begin{tabular}{|c|p{10cm}|p{5cm}|}
\hline
$k$ & Most Similar $k$ books & Average $a$ (Average Degree of Dissimilarity) \\\hline \hline
2 & Eph, Col & 2.361 \\ \hline
3 & \textbf{Rom},\textbf{ 1Cor}, \textbf{Gal} & 3.358 \\ \hline
4 & Rom, 1Cor, \textbf{2Cor}, Gal & 3.639 \\ \hline
5 & Rom, 1Cor, 2Cor, Gal, \textbf{2Tim} & 4.429 \\ \hline
6 & Rom, 2Cor, \textbf{Phil}, \textbf{1Thess}, \textbf{2Thess}, 2Tim & 4.826 \\ \hline
7 & Rom, \textbf{1Cor}, 2Cor, Phil, 1Thess, 2Thess, 2Tim & 5.204 \\ \hline
8 & Rom, 1Cor, 2Cor, \textbf{Gal}, Phil, 1Thess, 2Thess, 2Tim & 5.464 \\ \hline
9 & Rom, 1Cor, 2Cor, Gal, \textbf{Eph}, Phil, 1Thess, 2Thess, 2Tim & 5.804 \\ \hline
10 & Rom, 1Cor, 2Cor, Gal, Eph, Phil, \textbf{Col}, 1Thess, 2Thess, 2Tim & 6.253 \\ \hline
11 & Rom, 1Cor, 2Cor, Gal, Eph, Phil, Col, 1Thess, 2Thess, 2Tim, \textbf{Phlm} & 6.67 \\ \hline
12 & Rom, 1Cor, 2Cor, Gal, Eph, Phil, Col, 1Thess, 2Thess, 2Tim, \textbf{Titus}, Phlm & 7.101 \\ \hline
13 & Rom, 1Cor, 2Cor, Gal, Eph, Phil, Col, 1Thess, 2Thess, \textbf{1Tim}, 2Tim, Titus, Phlm & 7.410 \\ \hline
\end{tabular}
\end{center}

From this, we can order (approximately) the 13 books from most Pauline to least Pauline: Romans, 1 Corinthians, Galatians, 2 Corinthians, 2 Timothy, Philippians, 1 Thessalonians, 2 Thessalonians, Ephesians, Colossians, Philemon, Titus, and 1 Timothy.  

(Despite Ephesians and Colossians appearing first, I have chosen not to consider them most Pauline because they appear to only be similarly dissimilar.  We can pretty safely do this because a very clear in-group began to develop in $k = 3,4,5.$)

\subsection{Comparison to results of modern scholarship}

As stated above, modern scholarship believes that Romans, 1 Corinthians, 2 Corinthians, Galatians, Philippians, 1 Thessalonians, and Philemon are authentic.  Colossians and 2 Thessalonians are disputed, and Ephesians, 1 Timothy, 2 Timothy, and Titus are believed to be pseudepigraphic.  

The agreement with modern scholarship is very remarkable, especially considering that these determinations come from only the frequencies of the top 10-15 most common words in the books (words that, in English, would be words like the, he, is, and, but, for, etc).  

The notable outliers in our analysis are: 2 Timothy and Philemon.  

\subsubsection{2 Timothy}

Our analysis shows that \textbf{2 Timothy is much much more Pauline than modern scholarship thinks it is}.  Indeed, modern scholarship is much more divided on 2 Timothy than 1 Timothy and Titus, the two other pastoral epistles.  \textbf{Our analysis may be very revealing.}

Often, modern scholarship discounts the Pauline authorship of 2 Timothy by grouping 1 Timothy, 2 Timothy, and Titus into one collection and discounting all three of them at the same time.  However, our analysis shows significant differences between 2 Timothy and the other two books.  (As you can see in Appendix B, 1 Timothy and Titus are similar to each other but very different from the Pauline epistles, whereas 2 Timothy is far closer to the "authentic" Pauline epistles than it is to 1 Timothy.)  

These differences can be seen in the content of 2 Timothy, which aligns much better with more "traditional" Pauline concepts, compared to the overtly misognystic non-sola fide in 1 Timothy (2:15).  

Our analysis maintains the claim that 1 Timothy and Titus are not Pauline works but provides significant evidence against grouping 2 Timothy with the two other Pastoral Epistles. 

\subsubsection{Philemon}

Our analysis shows that \textbf{Philemon is much less Pauline than modern scholarship thinks it is}.  Modern scholarship rarely questions the authorship of Philemon, so it appears that \textbf{our analysis may have erred in this case.}  One possible reason is the book's shortness.  Almost all Pauline epistles have a greeting, introduction, thanksgiving, and conclusion, which contains a different style than the main body of the epistle.  Since Philemon is so short, the greeting, introduction, thanksgiving, and conclusion take up almost half of the entire epistle.  This can significantly skew the frequency counts, thereby causing a possible erroneous result.  

\subsection{Disclaimers (again)}
These are important disclaimers, so I will say them again.

Disclaimer 1: This was mostly a personal project to practice my programming skills.  I was surprised by the results, especially since I did not need to optimize anything to attain them.  Real algorithms to analyze authorship are (probably) more complex and reliable, so this shouldn't be considered a substitute for real scholarship.  

Disclaimer 2: Any information about current scholarly consensus should be taken with a grain of salt.  First of all, most outside information in this paper came from Wikipedia.  At the very best, it's a bad research practice and at the very worst, the information is wrong.  Also, please note that both Wikipedia and modern critical analysis are skewed against conservative religious thought due to the general overrepresentation of progressive scholarship in universities.  Modern scholars are extremely quick to reject claims to authorship on the basis of occasionally minute details.  

Disclaimer 3: For the Christian, rejecting the teachings of certain books because they are pseudepigraphic is dangerous business.  Many times, they are considered pseudepigraphic largely in part due to the presence of ``inconvenient'' doctrines (misogyny is the biggest culprit) or simply because it seems different.  


\section{Sources}
The Greek New Testament in csv format was downloaded from \underline{\href{https://github.com/biblicalhumanities/Nestle1904/tree/master/morph}{here}}.  

I made use of \underline{\href{http://kingjamesbibledictionary.com/}{this website}} to translate Strong's numbers to English (done in Appendix A).

Most of the information about New Testament scholarship was taken from these Wikipedia pages: \underline{\href{https://en.wikipedia.org/wiki/New_Testament}{New Testament}}, \underline{\href{https://en.wikipedia.org/wiki/Authorship_of_the_Pauline_epistles}{Authorship of the Pauline Epistles}}, \underline{\href{https://en.wikipedia.org/wiki/Authorship_of_the_Petrine_epistles}{Authorship of the Petrine Epistles}}, \underline{\href{https://en.wikipedia.org/wiki/Second_Epistle_to_Timothy}{Second Epistle to Timothy}}, \underline{\href{https://en.wikipedia.org/wiki/Epistle_to_Philemon}{Epistle to Philemon}}, \underline{\href{https://en.wikipedia.org/wiki/Authorship_of_the_Johannine_works}{Authorship of the Johannine works}}. 

In writing the section on 2 Timothy, I used these two articles from the New World Encyclopedia: \underline{\href{https://www.newworldencyclopedia.org/entry/Second_Epistle_to_Timothy}{Second Epistle to Timothy}} and \underline{\href{https://www.newworldencyclopedia.org/entry/First_Epistle_to_Timothy}{First Epistle to Timothy}}.  

\newpage 

\appendix
\section{Top Twenty Words in Each Book}

Matt


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.15164763101808842\\ \hline 
 2532, and & 0.0638832723099623\\ \hline 
 846, himself & 0.04967484561997924\\ \hline 
 1161, but & 0.026996010710967813\\ \hline 
 3004, say & 0.025903054811738345\\ \hline 
 4771, you & 0.02481009891250888\\ \hline 
 1772, in & 0.016011803923711678\\ \hline 
 1510, to be & 0.015738564948904313\\ \hline 
 1473, I & 0.01420842668998306\\ \hline 
 1519, into & 0.011858571506639708\\ \hline 
 3756, not & 0.011093502377179081\\ \hline 
 2424, Jesus & 0.008197169244220997\\ \hline 
 3778, this & 0.007978578064375103\\ \hline 
 3754, that & 0.007705339089567736\\ \hline 
 3708, see & 0.007486747909721842\\ \hline 
 3361, not lest & 0.007322804524837423\\ \hline 
 3956, all & 0.006994917755068583\\ \hline 
 3739, who & 0.006830974370184163\\ \hline 
 1063, for & 0.00677632657522269\\ \hline 
 1909, upon & 0.006667030985299743\\ \hline 
\end{longtable} 
 

Mark


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.1339895362241731\\ \hline 
 2532, and & 0.09621353196772191\\ \hline 
 846, himself & 0.0671277822115811\\ \hline 
 3004, say & 0.025450031036623216\\ \hline 
 1510, to be & 0.01711448080163164\\ \hline 
 1519, into & 0.0148975791433892\\ \hline 
 4771, you & 0.014542874878070409\\ \hline 
 1161, but & 0.01445419881174071\\ \hline 
 1772, in & 0.01223729715349827\\ \hline 
 1473, I & 0.011439212556530992\\ \hline 
 3756, not & 0.010641127959563713\\ \hline 
 3754, that & 0.009133634831958854\\ \hline 
 3739, who & 0.007714817770683693\\ \hline 
 2064, come & 0.007626141704353995\\ \hline 
 2424, Jesus & 0.007271437439035204\\ \hline 
 3778, this & 0.007005409240046111\\ \hline 
 3361, not lest & 0.006916733173716414\\ \hline 
 5101, what & 0.006384676775738229\\ \hline 
 1909, upon & 0.006384676775738229\\ \hline 
 2192, to have & 0.006207324643078833\\ \hline 
\end{longtable} 
 

Luke


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.13563939144736842\\ \hline 
 2532, and & 0.07529810855263158\\ \hline 
 846, himself & 0.05556126644736842\\ \hline 
 1161, but & 0.027857730263157895\\ \hline 
 3004, say & 0.0263671875\\ \hline 
 4771, you & 0.022872121710526317\\ \hline 
 1510, to be & 0.0185546875\\ \hline 
 1772, in & 0.01845189144736842\\ \hline 
 1473, I & 0.014494243421052632\\ \hline 
 3778, this & 0.01177014802631579\\ \hline 
 1519, into & 0.01166735197368421\\ \hline 
 3739, who & 0.009765625\\ \hline 
 3756, not & 0.008891858552631578\\ \hline 
 3754, that & 0.008891858552631578\\ \hline 
 4314, forward & 0.008532072368421052\\ \hline 
 1909, upon & 0.008275082236842105\\ \hline 
 3956, all & 0.008120888157894737\\ \hline 
 3361, not lest & 0.007401315789473684\\ \hline 
 3708, see & 0.007092927631578948\\ \hline 
 1096, made & 0.006630345394736842\\ \hline 
\end{longtable} 
 

John


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.13910375247714632\\ \hline 
 2532, and & 0.05312280253148373\\ \hline 
 846, himself & 0.04845617848238829\\ \hline 
 1473, I & 0.032666368343668095\\ \hline 
 3004, say & 0.03042894585437576\\ \hline 
 1510, to be & 0.028383302435594195\\ \hline 
 4771, you & 0.02614587994630186\\ \hline 
 3756, not & 0.017963306271175605\\ \hline 
 3754, that & 0.017260116345969443\\ \hline 
 2424, Jesus & 0.015534104711372499\\ \hline 
 3778, this & 0.015342325640861727\\ \hline 
 1772, in & 0.014447356645144793\\ \hline 
 1161, but & 0.013360608578917087\\ \hline 
 3767, then & 0.012657418653710926\\ \hline 
 1519, into & 0.012018155085341686\\ \hline 
 1537, out from & 0.010483922521255514\\ \hline 
 3739, who & 0.010292143450744742\\ \hline 
 2064, come & 0.010036438023397046\\ \hline 
 2443, in order that & 0.00926932174135396\\ \hline 
 3962, father & 0.008630058172984722\\ \hline 
\end{longtable} 
 

Acts


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.14603381721307018\\ \hline 
 2532, and & 0.06013157179361714\\ \hline 
 846, himself & 0.03767737726308922\\ \hline 
 1161, but & 0.030337628445604305\\ \hline 
 1473, I & 0.016636763986299135\\ \hline 
 1519, into & 0.016310552927744252\\ \hline 
 1510, to be & 0.015005708693524711\\ \hline 
 1772, in & 0.015005708693524711\\ \hline 
 4771, you & 0.014135812537378351\\ \hline 
 3778, this & 0.01283096830315881\\ \hline 
 3004, say & 0.012287283205567335\\ \hline 
 3739, who & 0.012232914695808188\\ \hline 
 3956, all & 0.009405752188332518\\ \hline 
 1909, upon & 0.00913390963953678\\ \hline 
 2316, God & 0.008970804110259337\\ \hline 
 5037, and & 0.007937802424835536\\ \hline 
 4314, forward & 0.007285380307725765\\ \hline 
 3972, Paul & 0.00695916924917088\\ \hline 
 1096, made & 0.006796063719893438\\ \hline 
 3754, that & 0.006687326700375143\\ \hline 
\end{longtable} 
 

Rom


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.15535211267605634\\ \hline 
 2532, and & 0.038450704225352114\\ \hline 
 1772, in & 0.02436619718309859\\ \hline 
 846, himself & 0.02211267605633803\\ \hline 
 2316, God & 0.02140845070422535\\ \hline 
 1473, I & 0.020985915492957745\\ \hline 
 1161, but & 0.020704225352112676\\ \hline 
 1063, for & 0.02028169014084507\\ \hline 
 4771, you & 0.018028169014084508\\ \hline 
 3756, not & 0.017183098591549296\\ \hline 
 1519, into & 0.01676056338028169\\ \hline 
 1510, to be & 0.01591549295774648\\ \hline 
 1223, through & 0.012816901408450704\\ \hline 
 3739, who & 0.012816901408450704\\ \hline 
 3361, not lest & 0.011126760563380281\\ \hline 
 3551, law & 0.010422535211267606\\ \hline 
 3956, all & 0.009859154929577466\\ \hline 
 235, but & 0.009718309859154929\\ \hline 
 5547, Christ & 0.009154929577464789\\ \hline 
 1537, out from & 0.008450704225352112\\ \hline 
\end{longtable} 
 

1Cor


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.12683284457478006\\ \hline 
 2532, and & 0.04090909090909091\\ \hline 
 1161, but & 0.030791788856304986\\ \hline 
 1772, in & 0.024780058651026393\\ \hline 
 1510, to be & 0.023607038123167154\\ \hline 
 3756, not & 0.02287390029325513\\ \hline 
 4771, you & 0.02258064516129032\\ \hline 
 1473, I & 0.0187683284457478\\ \hline 
 3956, all & 0.016422287390029325\\ \hline 
 1063, for & 0.015542521994134898\\ \hline 
 2316, God & 0.015395894428152493\\ \hline 
 3361, not lest & 0.01407624633431085\\ \hline 
 846, himself & 0.012609970674486803\\ \hline 
 235, but & 0.010557184750733138\\ \hline 
 3778, this & 0.00997067448680352\\ \hline 
 2962, supreme & 0.009824046920821115\\ \hline 
 5547, Christ & 0.009237536656891495\\ \hline 
 1487, if & 0.009237536656891495\\ \hline 
 3739, who & 0.008944281524926686\\ \hline 
 3754, that & 0.008797653958944282\\ \hline 
\end{longtable} 
 

2Cor


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.12329380174535691\\ \hline 
 2532, and & 0.04408144998881181\\ \hline 
 1772, in & 0.036025956589841125\\ \hline 
 1473, I & 0.036025956589841125\\ \hline 
 4771, you & 0.03490713806220631\\ \hline 
 3756, not & 0.021705079436115462\\ \hline 
 2316, God & 0.01767733273663012\\ \hline 
 1519, into & 0.017453569031103153\\ \hline 
 1063, for & 0.016782277914522265\\ \hline 
 1161, but & 0.0165585142089953\\ \hline 
 235, but & 0.01521593197583352\\ \hline 
 846, himself & 0.013873349742671738\\ \hline 
 1510, to be & 0.013873349742671738\\ \hline 
 3956, all & 0.011635712687402103\\ \hline 
 3754, that & 0.01141194898187514\\ \hline 
 3361, not lest & 0.010964421570821213\\ \hline 
 5547, Christ & 0.010516894159767285\\ \hline 
 1223, through & 0.010069366748713358\\ \hline 
 2443, in order that & 0.009845603043186395\\ \hline 
 3778, this & 0.009621839337659432\\ \hline 
\end{longtable} 
 

Gal


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.12387791741472172\\ \hline 
 2532, and & 0.03231597845601436\\ \hline 
 1473, I & 0.026481149012567325\\ \hline 
 1161, but & 0.026032315978456014\\ \hline 
 1510, to be & 0.02378815080789946\\ \hline 
 4771, you & 0.02333931777378815\\ \hline 
 1772, in & 0.018402154398563735\\ \hline 
 5547, Christ & 0.017055655296229804\\ \hline 
 3756, not & 0.017055655296229804\\ \hline 
 1063, for & 0.01615798922800718\\ \hline 
 1537, out from & 0.01570915619389587\\ \hline 
 3551, law & 0.01436265709156194\\ \hline 
 2316, God & 0.013464991023339317\\ \hline 
 1519, into & 0.013464991023339317\\ \hline 
 3754, that & 0.013016157989228007\\ \hline 
 846, himself & 0.011669658886894075\\ \hline 
 3361, not lest & 0.010771992818671455\\ \hline 
 3739, who & 0.010323159784560144\\ \hline 
 235, but & 0.010323159784560144\\ \hline 
 4102, faith & 0.009874326750448833\\ \hline 
\end{longtable} 
 

Eph


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.17858619264158743\\ \hline 
 2532, and & 0.05663497312939231\\ \hline 
 1772, in & 0.05002066969822241\\ \hline 
 846, himself & 0.02728400165357586\\ \hline 
 3956, all & 0.02108309218685407\\ \hline 
 4771, you & 0.020256304257957835\\ \hline 
 1510, to be & 0.019842910293509715\\ \hline 
 5547, Christ & 0.019016122364613478\\ \hline 
 1473, I & 0.017775940471269118\\ \hline 
 1519, into & 0.015295576684580404\\ \hline 
 3739, who & 0.01364200082678793\\ \hline 
 2316, God & 0.012815212897891691\\ \hline 
 2962, supreme & 0.010748243075651096\\ \hline 
 2596, according & 0.009921455146754857\\ \hline 
 2443, in order that & 0.009508061182306739\\ \hline 
 1223, through & 0.0086812732534105\\ \hline 
 1161, but & 0.00826787928896238\\ \hline 
 2424, Jesus & 0.00826787928896238\\ \hline 
 3778, this & 0.007441091360066143\\ \hline 
 3361, not lest & 0.006614303431169905\\ \hline 
\end{longtable} 
 

Phil


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.11779141104294479\\ \hline 
 2532, and & 0.0656441717791411\\ \hline 
 1772, in & 0.03987730061349693\\ \hline 
 1473, I & 0.03558282208588957\\ \hline 
 4771, you & 0.03190184049079755\\ \hline 
 5547, Christ & 0.022699386503067485\\ \hline 
 3956, all & 0.020245398773006136\\ \hline 
 846, himself & 0.01901840490797546\\ \hline 
 1161, but & 0.016564417177914112\\ \hline 
 2316, God & 0.014723926380368098\\ \hline 
 1519, into & 0.01411042944785276\\ \hline 
 2424, Jesus & 0.013496932515337423\\ \hline 
 3754, that & 0.012883435582822086\\ \hline 
 1510, to be & 0.010429447852760737\\ \hline 
 3739, who & 0.009202453987730062\\ \hline 
 2962, supreme & 0.009202453987730062\\ \hline 
 3778, this & 0.009202453987730062\\ \hline 
 235, but & 0.009202453987730062\\ \hline 
 1223, through & 0.008588957055214725\\ \hline 
 1487, if & 0.007975460122699387\\ \hline 
\end{longtable} 
 

Col


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.16444444444444445\\ \hline 
 2532, and & 0.06412698412698413\\ \hline 
 1772, in & 0.05523809523809524\\ \hline 
 4771, you & 0.035555555555555556\\ \hline 
 846, himself & 0.02857142857142857\\ \hline 
 3956, all & 0.024761904761904763\\ \hline 
 3739, who & 0.02412698412698413\\ \hline 
 1510, to be & 0.01650793650793651\\ \hline 
 5547, Christ & 0.015873015873015872\\ \hline 
 1473, I & 0.015873015873015872\\ \hline 
 2316, God & 0.013333333333333334\\ \hline 
 1519, into & 0.012063492063492064\\ \hline 
 2962, supreme & 0.010158730158730159\\ \hline 
 1223, through & 0.008888888888888889\\ \hline 
 2596, according & 0.008888888888888889\\ \hline 
 2443, in order that & 0.008253968253968255\\ \hline 
 1537, out from & 0.006984126984126984\\ \hline 
 3361, not lest & 0.006349206349206349\\ \hline 
 575, from & 0.005714285714285714\\ \hline 
 4561, flesh & 0.005714285714285714\\ \hline 
\end{longtable} 
 

1Thess


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.1296673455532926\\ \hline 
 2532, and & 0.06788866259334692\\ \hline 
 4771, you & 0.05702647657841141\\ \hline 
 1772, in & 0.03598099117447386\\ \hline 
 1473, I & 0.03394433129667346\\ \hline 
 2316, God & 0.024439918533604887\\ \hline 
 1519, into & 0.017651052274270197\\ \hline 
 2962, supreme & 0.016293279022403257\\ \hline 
 846, himself & 0.016293279022403257\\ \hline 
 1063, for & 0.015614392396469789\\ \hline 
 80, brother & 0.012898845892735914\\ \hline 
 3756, not & 0.012219959266802444\\ \hline 
 3956, all & 0.012219959266802444\\ \hline 
 2424, Jesus & 0.010862186014935505\\ \hline 
 1161, but & 0.010183299389002037\\ \hline 
 3361, not lest & 0.010183299389002037\\ \hline 
 2531, as & 0.008825526137135099\\ \hline 
 3754, that & 0.008825526137135099\\ \hline 
 235, but & 0.008825526137135099\\ \hline 
 1492, know & 0.008825526137135099\\ \hline 
\end{longtable} 
 

2Thess


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.1362530413625304\\ \hline 
 2532, and & 0.06082725060827251\\ \hline 
 4771, you & 0.04866180048661801\\ \hline 
 1772, in & 0.031630170316301706\\ \hline 
 1473, I & 0.029197080291970802\\ \hline 
 2962, supreme & 0.0267639902676399\\ \hline 
 846, himself & 0.021897810218978103\\ \hline 
 2316, God & 0.021897810218978103\\ \hline 
 3956, all & 0.019464720194647202\\ \hline 
 1519, into & 0.0170316301703163\\ \hline 
 2424, Jesus & 0.015815085158150853\\ \hline 
 3739, who & 0.014598540145985401\\ \hline 
 3361, not lest & 0.01338199513381995\\ \hline 
 3754, that & 0.01338199513381995\\ \hline 
 1161, but & 0.01338199513381995\\ \hline 
 5547, Christ & 0.012165450121654502\\ \hline 
 1223, through & 0.012165450121654502\\ \hline 
 575, from & 0.010948905109489052\\ \hline 
 80, brother & 0.010948905109489052\\ \hline 
 3756, not & 0.009732360097323601\\ \hline 
\end{longtable} 
 

1Tim


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.09949622166246852\\ \hline 
 2532, and & 0.05793450881612091\\ \hline 
 1772, in & 0.02707808564231738\\ \hline 
 1161, but & 0.018891687657430732\\ \hline 
 1510, to be & 0.018261964735516372\\ \hline 
 3361, not lest & 0.015113350125944584\\ \hline 
 3956, all & 0.014483627204030227\\ \hline 
 3739, who & 0.013853904282115869\\ \hline 
 2316, God & 0.013853904282115869\\ \hline 
 4102, faith & 0.011964735516372796\\ \hline 
 1519, into & 0.011964735516372796\\ \hline 
 3778, this & 0.011335012594458438\\ \hline 
 5100, some & 0.011335012594458438\\ \hline 
 2570, good & 0.010075566750629723\\ \hline 
 2443, in order that & 0.009445843828715366\\ \hline 
 5547, Christ & 0.009445843828715366\\ \hline 
 1473, I & 0.009445843828715366\\ \hline 
 4771, you & 0.008816120906801008\\ \hline 
 2192, to have & 0.008816120906801008\\ \hline 
 2424, Jesus & 0.008816120906801008\\ \hline 
\end{longtable} 
 

2Tim


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.12045270816491511\\ \hline 
 2532, and & 0.0549717057396928\\ \hline 
 1473, I & 0.03395311236863379\\ \hline 
 1772, in & 0.029911075181891674\\ \hline 
 1161, but & 0.019401778496362168\\ \hline 
 4771, you & 0.016976556184316895\\ \hline 
 3739, who & 0.016168148746968473\\ \hline 
 1519, into & 0.014551333872271624\\ \hline 
 3956, all & 0.014551333872271624\\ \hline 
 2962, supreme & 0.012934518997574777\\ \hline 
 846, himself & 0.012934518997574777\\ \hline 
 1510, to be & 0.012934518997574777\\ \hline 
 1063, for & 0.01131770412287793\\ \hline 
 5547, Christ & 0.010509296685529508\\ \hline 
 2424, Jesus & 0.010509296685529508\\ \hline 
 2316, God & 0.010509296685529508\\ \hline 
 1223, through & 0.009700889248181084\\ \hline 
 235, but & 0.009700889248181084\\ \hline 
 3756, not & 0.009700889248181084\\ \hline 
 3778, this & 0.00889248181083266\\ \hline 
\end{longtable} 
 

Titus


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.09270516717325228\\ \hline 
 2532, and & 0.0547112462006079\\ \hline 
 1473, I & 0.028875379939209727\\ \hline 
 1510, to be & 0.0243161094224924\\ \hline 
 3956, all & 0.02127659574468085\\ \hline 
 3361, not lest & 0.019756838905775075\\ \hline 
 2443, in order that & 0.019756838905775075\\ \hline 
 1772, in & 0.019756838905775075\\ \hline 
 2316, God & 0.019756838905775075\\ \hline 
 3739, who & 0.013677811550151976\\ \hline 
 4771, you & 0.0121580547112462\\ \hline 
 2041, work & 0.0121580547112462\\ \hline 
 1161, but & 0.0121580547112462\\ \hline 
 846, himself & 0.0121580547112462\\ \hline 
 2596, according & 0.0121580547112462\\ \hline 
 4102, faith & 0.00911854103343465\\ \hline 
 4990, savior & 0.00911854103343465\\ \hline 
 1063, for & 0.00911854103343465\\ \hline 
 3778, this & 0.007598784194528876\\ \hline 
 3056, word & 0.007598784194528876\\ \hline 
\end{longtable} 
 

Phlm


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.10746268656716418\\ \hline 
 4771, you & 0.07164179104477612\\ \hline 
 1473, I & 0.0626865671641791\\ \hline 
 2532, and & 0.05373134328358209\\ \hline 
 1772, in & 0.029850746268656716\\ \hline 
 5547, Christ & 0.023880597014925373\\ \hline 
 1161, but & 0.01791044776119403\\ \hline 
 2424, Jesus & 0.01791044776119403\\ \hline 
 3739, who & 0.014925373134328358\\ \hline 
 2962, supreme & 0.014925373134328358\\ \hline 
 1223, through & 0.011940298507462687\\ \hline 
 3754, that & 0.011940298507462687\\ \hline 
 2443, in order that & 0.011940298507462687\\ \hline 
 80, brother & 0.011940298507462687\\ \hline 
 2192, to have & 0.011940298507462687\\ \hline 
 5613, as & 0.011940298507462687\\ \hline 
 3778, this & 0.008955223880597015\\ \hline 
 4160, make & 0.008955223880597015\\ \hline 
 4968, bowels & 0.008955223880597015\\ \hline 
 3972, Paul & 0.008955223880597015\\ \hline 
\end{longtable} 
 

Heb


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.1408678102926337\\ \hline 
 2532, and & 0.05126135216952573\\ \hline 
 846, himself & 0.028456104944500505\\ \hline 
 1063, for & 0.018365287588294654\\ \hline 
 1519, into & 0.014934409687184663\\ \hline 
 3739, who & 0.014934409687184663\\ \hline 
 1161, but & 0.013925327951564077\\ \hline 
 2316, God & 0.013723511604439959\\ \hline 
 3756, not & 0.013319878910191726\\ \hline 
 1473, I & 0.013319878910191726\\ \hline 
 1772, in & 0.013118062563067608\\ \hline 
 4771, you & 0.011907164480322906\\ \hline 
 1223, through & 0.011503531786074672\\ \hline 
 1510, to be & 0.011099899091826439\\ \hline 
 3956, all & 0.010696266397578204\\ \hline 
 3778, this & 0.00887991927346115\\ \hline 
 3361, not lest & 0.00887991927346115\\ \hline 
 2596, according & 0.008274470232088799\\ \hline 
 2192, to have & 0.007870837537840566\\ \hline 
 3004, say & 0.007669021190716448\\ \hline 
\end{longtable} 
 

Jas


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.13225991949396204\\ \hline 
 2532, and & 0.06325474410580793\\ \hline 
 4771, you & 0.02702702702702703\\ \hline 
 846, himself & 0.023001725129384705\\ \hline 
 1772, in & 0.02185163887291547\\ \hline 
 1161, but & 0.02127659574468085\\ \hline 
 1510, to be & 0.018401380103507763\\ \hline 
 3756, not & 0.015526164462334674\\ \hline 
 3361, not lest & 0.013801035077630822\\ \hline 
 1473, I & 0.012650948821161587\\ \hline 
 80, brother & 0.010925819436457734\\ \hline 
 2316, God & 0.009200690051753882\\ \hline 
 4102, faith & 0.009200690051753882\\ \hline 
 3754, that & 0.009200690051753882\\ \hline 
 1519, into & 0.008625646923519264\\ \hline 
 2041, work & 0.008625646923519264\\ \hline 
 5100, some & 0.008625646923519264\\ \hline 
 1063, for & 0.008625646923519264\\ \hline 
 2962, supreme & 0.008050603795284647\\ \hline 
 1537, out from & 0.007475560667050029\\ \hline 
\end{longtable} 
 

1Pet


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.11813842482100238\\ \hline 
 2532, and & 0.042362768496420046\\ \hline 
 4771, you & 0.031026252983293555\\ \hline 
 1772, in & 0.029832935560859187\\ \hline 
 1519, into & 0.025059665871121718\\ \hline 
 2316, God & 0.023269689737470168\\ \hline 
 846, himself & 0.02028639618138425\\ \hline 
 3739, who & 0.018496420047732696\\ \hline 
 1161, but & 0.016706443914081145\\ \hline 
 5613, as & 0.016109785202863963\\ \hline 
 5547, Christ & 0.013126491646778043\\ \hline 
 3956, all & 0.010739856801909307\\ \hline 
 1223, through & 0.010739856801909307\\ \hline 
 235, but & 0.00954653937947494\\ \hline 
 1487, if & 0.008949880668257757\\ \hline 
 3754, that & 0.008949880668257757\\ \hline 
 3361, not lest & 0.008353221957040573\\ \hline 
 2443, in order that & 0.007756563245823389\\ \hline 
 3756, not & 0.007756563245823389\\ \hline 
 3778, this & 0.0065632458233890216\\ \hline 
\end{longtable} 
 

2Pet


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.11293260473588343\\ \hline 
 2532, and & 0.05737704918032787\\ \hline 
 1772, in & 0.039162112932604735\\ \hline 
 846, himself & 0.026411657559198543\\ \hline 
 3778, this & 0.020036429872495445\\ \hline 
 4771, you & 0.01912568306010929\\ \hline 
 1161, but & 0.01912568306010929\\ \hline 
 3739, who & 0.017304189435336976\\ \hline 
 1473, I & 0.017304189435336976\\ \hline 
 1063, for & 0.01366120218579235\\ \hline 
 2962, supreme & 0.012750455373406194\\ \hline 
 1510, to be & 0.011839708561020037\\ \hline 
 3756, not & 0.01092896174863388\\ \hline 
 2250, day & 0.01092896174863388\\ \hline 
 1519, into & 0.010018214936247723\\ \hline 
 5613, as & 0.009107468123861567\\ \hline 
 2424, Jesus & 0.00819672131147541\\ \hline 
 5547, Christ & 0.007285974499089253\\ \hline 
 3956, all & 0.006375227686703097\\ \hline 
 1223, through & 0.006375227686703097\\ \hline 
\end{longtable} 
 

1John


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.16807116104868913\\ \hline 
 2532, and & 0.060393258426966294\\ \hline 
 846, himself & 0.047752808988764044\\ \hline 
 1510, to be & 0.046348314606741575\\ \hline 
 1772, in & 0.03698501872659176\\ \hline 
 3754, that & 0.035580524344569285\\ \hline 
 2316, God & 0.02902621722846442\\ \hline 
 1473, I & 0.026217228464419477\\ \hline 
 3756, not & 0.02247191011235955\\ \hline 
 3778, this & 0.018258426966292134\\ \hline 
 4771, you & 0.015917602996254682\\ \hline 
 1537, out from & 0.015917602996254682\\ \hline 
 3739, who & 0.014044943820224719\\ \hline 
 2192, to have & 0.013108614232209739\\ \hline 
 25, to love & 0.013108614232209739\\ \hline 
 3956, all & 0.012640449438202247\\ \hline 
 1097, to know & 0.011704119850187267\\ \hline 
 3306, to stay & 0.011235955056179775\\ \hline 
 2889, world & 0.010767790262172285\\ \hline 
 1437, if & 0.010299625468164793\\ \hline 
\end{longtable} 
 

2John


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.1346938775510204\\ \hline 
 2532, and & 0.0653061224489796\\ \hline 
 4771, you & 0.0326530612244898\\ \hline 
 1772, in & 0.0326530612244898\\ \hline 
 846, himself & 0.02857142857142857\\ \hline 
 1473, I & 0.024489795918367346\\ \hline 
 1510, to be & 0.024489795918367346\\ \hline 
 3361, not lest & 0.02040816326530612\\ \hline 
 3756, not & 0.02040816326530612\\ \hline 
 225, truth & 0.02040816326530612\\ \hline 
 3778, this & 0.02040816326530612\\ \hline 
 2443, in order that & 0.02040816326530612\\ \hline 
 1785, commandment & 0.0163265306122449\\ \hline 
 3962, father & 0.0163265306122449\\ \hline 
 2192, to have & 0.0163265306122449\\ \hline 
 235, but & 0.0163265306122449\\ \hline 
 5547, Christ & 0.012244897959183673\\ \hline 
 3306, to stay & 0.012244897959183673\\ \hline 
 4314, forward & 0.012244897959183673\\ \hline 
 1519, into & 0.012244897959183673\\ \hline 
\end{longtable} 
 

3John


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.1324200913242009\\ \hline 
 2532, and & 0.0502283105022831\\ \hline 
 4771, you & 0.045662100456621\\ \hline 
 1473, I & 0.0273972602739726\\ \hline 
 225, truth & 0.0273972602739726\\ \hline 
 3739, who & 0.0228310502283105\\ \hline 
 3140, to witness & 0.0182648401826484\\ \hline 
 3778, this & 0.0182648401826484\\ \hline 
 3756, not & 0.0182648401826484\\ \hline 
 846, himself & 0.0182648401826484\\ \hline 
 27, beloved & 0.0182648401826484\\ \hline 
 1125, write & 0.0136986301369863\\ \hline 
 80, brother & 0.0136986301369863\\ \hline 
 1577, church & 0.0136986301369863\\ \hline 
 235, but & 0.0136986301369863\\ \hline 
 2316, God & 0.0136986301369863\\ \hline 
 1772, in & 0.0136986301369863\\ \hline 
 4160, make & 0.0136986301369863\\ \hline 
 3686, name & 0.0091324200913242\\ \hline 
 3708, see & 0.0091324200913242\\ \hline 
\end{longtable} 
 

Jude


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.12035010940919037\\ \hline 
 2532, and & 0.045951859956236324\\ \hline 
 1161, but & 0.0262582056892779\\ \hline 
 4771, you & 0.024070021881838075\\ \hline 
 3778, this & 0.019693654266958426\\ \hline 
 1772, in & 0.0175054704595186\\ \hline 
 3956, all & 0.0175054704595186\\ \hline 
 846, himself & 0.0175054704595186\\ \hline 
 1473, I & 0.015317286652078774\\ \hline 
 2962, supreme & 0.015317286652078774\\ \hline 
 2424, Jesus & 0.01312910284463895\\ \hline 
 1438, himself & 0.01312910284463895\\ \hline 
 5547, Christ & 0.01312910284463895\\ \hline 
 1519, into & 0.01312910284463895\\ \hline 
 4012, about & 0.010940919037199124\\ \hline 
 5083, guard & 0.010940919037199124\\ \hline 
 3739, who & 0.010940919037199124\\ \hline 
 40, sacred& 0.0087527352297593\\ \hline 
 2316, God & 0.0087527352297593\\ \hline 
 1510, to be & 0.0087527352297593\\ \hline 
\end{longtable} 
 

Rev


 \begin{longtable}{|c|c|}
\hline
 Strong's No., English & Frequency \\ \hline  
3588, this & 0.19172091131000812\\ \hline 
 2532, and & 0.1136086248982913\\ \hline 
 846, himself & 0.04465012205044752\\ \hline 
 1772, in & 0.016069975589910496\\ \hline 
 1909, upon & 0.014646053702196907\\ \hline 
 1537, out from & 0.013730675345809601\\ \hline 
 1510, to be & 0.011187957689178194\\ \hline 
 2192, to have & 0.01017087062652563\\ \hline 
 3004, say & 0.01017087062652563\\ \hline 
 1473, I & 0.00986574450772986\\ \hline 
 2316, God & 0.009662327095199348\\ \hline 
 3708, see & 0.009052074857607811\\ \hline 
 1093, land & 0.008340113913751017\\ \hline 
 3173, great & 0.008136696501220505\\ \hline 
 1519, into & 0.008136696501220505\\ \hline 
 4771, you & 0.008136696501220505\\ \hline 
 3739, who & 0.007119609438567941\\ \hline 
 5613, as & 0.007017900732302685\\ \hline 
 32, angel & 0.006814483319772173\\ \hline 
 3756, not & 0.006814483319772173\\ \hline 
\end{longtable} 
 



\newpage
\section{Book Similarities between all 27 books}

Matt
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Luke & 1.2498858510252246 \\ \hline
 Mark & 2.808491884758681 \\ \hline
 Acts & 2.863939222914629 \\ \hline
 Jas & 4.4346324976013465 \\ \hline
 John & 4.678567860690274 \\ \hline
 Jude & 6.961803874406476 \\ \hline
 Heb & 7.88402478953559 \\ \hline
 1Cor & 8.27718596926664 \\ \hline
 Rom & 8.344439915059338 \\ \hline
 2Pet & 9.082797677205104 \\ \hline
 Gal & 9.693678966679508 \\ \hline
 2Tim & 9.785473187567574 \\ \hline
 Eph & 10.432615562269314 \\ \hline
 Rev & 10.503923386527115 \\ \hline
 2Cor & 10.569479552521868 \\ \hline
 1Pet & 11.01860472708464 \\ \hline
 2John & 11.411612200679972 \\ \hline
 2Thess & 12.009534851244338 \\ \hline
 Col & 12.526479987093426 \\ \hline
 Phil & 12.982965547698754 \\ \hline
 1Thess & 13.166040445500222 \\ \hline
 1John & 13.319468398025837 \\ \hline
 Phlm & 14.564184398991955 \\ \hline
 1Tim & 15.001133513719347 \\ \hline
 Titus & 15.37829088943846 \\ \hline
 3John & 19.944348788153366 \\ \hline 
\end{longtable}


Mark
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Matt & 2.808491884758681 \\ \hline
 Luke & 3.0822798286148467 \\ \hline
 Acts & 4.037392272772234 \\ \hline
 John & 5.65640388695672 \\ \hline
 Jas & 6.182932982948504 \\ \hline
 Heb & 6.841319253495689 \\ \hline
 Rev & 9.052949729869212 \\ \hline
 Rom & 9.224729133939874 \\ \hline
 Jude & 10.453955571142572 \\ \hline
 2Pet & 10.584373854975077 \\ \hline
 1Cor & 10.81424890587908 \\ \hline
 1Pet & 11.240397808725703 \\ \hline
 2Cor & 11.416286750616639 \\ \hline
 Eph & 11.478587930258778 \\ \hline
 2Tim & 11.516673884347284 \\ \hline
 2John & 11.563196454726096 \\ \hline
 Gal & 12.224830001939202 \\ \hline
 1John & 13.325773953034545 \\ \hline
 2Thess & 13.55507990735967 \\ \hline
 3John & 13.581649263068126 \\ \hline
 Titus & 14.109114845386244 \\ \hline
 Phil & 14.217385143550265 \\ \hline
 Col & 14.342928234537267 \\ \hline
 1Thess & 14.585334331558329 \\ \hline
 1Tim & 14.731344772719343 \\ \hline
 Phlm & 17.67813790680798 \\ \hline 
\end{longtable}


Luke
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Matt & 1.2498858510252246 \\ \hline
 Acts & 2.9954302131011126 \\ \hline
 Mark & 3.0822798286148467 \\ \hline
 Jas & 5.291714777343677 \\ \hline
 John & 5.870433429065313 \\ \hline
 Jude & 6.473497387400187 \\ \hline
 1Cor & 7.820456175164511 \\ \hline
 Heb & 8.067114764522275 \\ \hline
 Rom & 8.516943816226547 \\ \hline
 2Pet & 8.62071208429699 \\ \hline
 2Tim & 9.519565236668662 \\ \hline
 1Pet & 10.589280497236954 \\ \hline
 2Cor & 10.793233528392742 \\ \hline
 2John & 10.996672989658158 \\ \hline
 Gal & 11.148630974497753 \\ \hline
 Rev & 11.15379430845007 \\ \hline
 1John & 11.17264101763682 \\ \hline
 Eph & 11.197209346847472 \\ \hline
 2Thess & 12.04492799547027 \\ \hline
 Phil & 12.728676716661727 \\ \hline
 Titus & 12.83754770994 \\ \hline
 1Thess & 13.204306172337871 \\ \hline
 1Tim & 13.302681404703307 \\ \hline
 Col & 13.670925587289256 \\ \hline
 Phlm & 14.904853202539176 \\ \hline
 3John & 18.053114680370125 \\ \hline 
\end{longtable}


John
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Matt & 4.678567860690274 \\ \hline
 Mark & 5.65640388695672 \\ \hline
 Luke & 5.870433429065313 \\ \hline
 Acts & 8.078242143693412 \\ \hline
 1John & 8.411323797616504 \\ \hline
 2John & 8.609675216567437 \\ \hline
 Jas & 8.721868817722687 \\ \hline
 3John & 10.265949844393411 \\ \hline
 Rom & 10.309927511788267 \\ \hline
 Gal & 10.404714409545871 \\ \hline
 1Cor & 10.907198570530603 \\ \hline
 2Cor & 11.061894508320831 \\ \hline
 Heb & 11.210480742875674 \\ \hline
 Jude & 11.469453846497478 \\ \hline
 2Pet & 12.024894659343758 \\ \hline
 2Tim & 12.148982543463408 \\ \hline
 2Thess & 12.46014091223983 \\ \hline
 Phlm & 12.762588361337974 \\ \hline
 Rev & 12.775960411976842 \\ \hline
 1Pet & 13.477308495380738 \\ \hline
 Phil & 13.49163960435913 \\ \hline
 Eph & 13.492052186245019 \\ \hline
 1Thess & 13.71369308283147 \\ \hline
 1Tim & 14.946319353391026 \\ \hline
 Col & 15.799653009352925 \\ \hline
 Titus & 16.259662280026276 \\ \hline 
\end{longtable}


Acts
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Matt & 2.863939222914629 \\ \hline
 Luke & 2.9954302131011126 \\ \hline
 Mark & 4.037392272772234 \\ \hline
 Jude & 4.916097429993837 \\ \hline
 2Pet & 5.082873396765076 \\ \hline
 Heb & 5.416026847796947 \\ \hline
 2Tim & 5.528398577945508 \\ \hline
 Jas & 6.472835406060057 \\ \hline
 Rom & 6.505012963443187 \\ \hline
 1Cor & 7.687001356338429 \\ \hline
 Eph & 7.847942989942897 \\ \hline
 John & 8.078242143693412 \\ \hline
 2Cor & 8.397518606367868 \\ \hline
 2Thess & 8.711506654093402 \\ \hline
 Phil & 9.061621886988657 \\ \hline
 1Pet & 9.629174665717688 \\ \hline
 Gal & 9.700489665529872 \\ \hline
 1Thess & 9.789277095129279 \\ \hline
 Col & 10.418140064290256 \\ \hline
 1Tim & 10.567553742690878 \\ \hline
 1John & 10.738945261034436 \\ \hline
 Rev & 11.117753366041498 \\ \hline
 2John & 11.486116236413995 \\ \hline
 Titus & 12.743731064008266 \\ \hline
 Phlm & 13.471742486015694 \\ \hline
 3John & 16.380265256484805 \\ \hline 
\end{longtable}


Rom
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
2Cor & 3.304624866250097 \\ \hline
 1Cor & 3.3634385915073337 \\ \hline
 Heb & 3.589732464510037 \\ \hline
 Gal & 3.762412087232254 \\ \hline
 Jas & 3.9067570184953815 \\ \hline
 2Pet & 5.068264652963615 \\ \hline
 2Tim & 5.347651691181487 \\ \hline
 1Thess & 5.562672736939286 \\ \hline
 Acts & 6.505012963443187 \\ \hline
 Phil & 6.559658832524622 \\ \hline
 2Thess & 6.597659163278408 \\ \hline
 1Pet & 7.751629182606049 \\ \hline
 Eph & 7.797311634922189 \\ \hline
 Matt & 8.344439915059338 \\ \hline
 1Tim & 8.444144360376796 \\ \hline
 Luke & 8.516943816226547 \\ \hline
 2John & 8.643309820482035 \\ \hline
 Jude & 8.81927986491159 \\ \hline
 Mark & 9.224729133939874 \\ \hline
 Titus & 9.601923689084177 \\ \hline
 Phlm & 9.771174850275099 \\ \hline
 Col & 9.98144735009302 \\ \hline
 1John & 10.30088385814545 \\ \hline
 John & 10.309927511788267 \\ \hline
 3John & 13.368059306084888 \\ \hline
 Rev & 15.409420118108146 \\ \hline 
\end{longtable}


1Cor
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Gal & 2.947045962736011 \\ \hline
 Rom & 3.3634385915073337 \\ \hline
 Jas & 4.260601660084346 \\ \hline
 2Cor & 4.470531192075281 \\ \hline
 2Tim & 5.599865151542004 \\ \hline
 2Pet & 6.236601819943239 \\ \hline
 Phil & 6.8095621465672505 \\ \hline
 Heb & 7.061425841167152 \\ \hline
 Jude & 7.0657256993816775 \\ \hline
 Acts & 7.687001356338429 \\ \hline
 Luke & 7.820456175164511 \\ \hline
 1Thess & 7.895460709124209 \\ \hline
 Titus & 8.199243241982249 \\ \hline
 Matt & 8.27718596926664 \\ \hline
 1Tim & 8.283817030355692 \\ \hline
 Eph & 8.619380545971659 \\ \hline
 2Thess & 8.761443809163133 \\ \hline
 2John & 9.057562497589577 \\ \hline
 Phlm & 9.486700703180663 \\ \hline
 Col & 10.43528571770649 \\ \hline
 1Pet & 10.801428149132054 \\ \hline
 Mark & 10.81424890587908 \\ \hline
 John & 10.907198570530603 \\ \hline
 1John & 10.964978350169366 \\ \hline
 3John & 16.707154203096355 \\ \hline
 Rev & 17.659429830249145 \\ \hline 
\end{longtable}


2Cor
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Rom & 3.304624866250097 \\ \hline
 1Thess & 3.5831709969695367 \\ \hline
 Gal & 3.9831036963231763 \\ \hline
 1Cor & 4.470531192075281 \\ \hline
 Phil & 4.507446899462842 \\ \hline
 2Tim & 4.72576351900792 \\ \hline
 Heb & 5.707156188036583 \\ \hline
 2Thess & 5.750838561889809 \\ \hline
 Jas & 5.860917943917871 \\ \hline
 2Pet & 6.368628606851557 \\ \hline
 1Pet & 7.306147537348039 \\ \hline
 2John & 7.9806914148624415 \\ \hline
 Phlm & 8.268911865836756 \\ \hline
 Acts & 8.397518606367868 \\ \hline
 Eph & 8.437749735109865 \\ \hline
 Jude & 9.317805067829227 \\ \hline
 1Tim & 9.53777224016234 \\ \hline
 Col & 10.172539684962665 \\ \hline
 Matt & 10.569479552521868 \\ \hline
 Titus & 10.640134011635926 \\ \hline
 Luke & 10.793233528392742 \\ \hline
 John & 11.061894508320831 \\ \hline
 Mark & 11.416286750616639 \\ \hline
 1John & 11.669816665478802 \\ \hline
 3John & 13.617121499640714 \\ \hline
 Rev & 18.032964178582887 \\ \hline 
\end{longtable}


Gal
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
1Cor & 2.947045962736011 \\ \hline
 Rom & 3.762412087232254 \\ \hline
 2Cor & 3.9831036963231763 \\ \hline
 Jas & 6.597426691669961 \\ \hline
 2Tim & 6.785928983326744 \\ \hline
 Phil & 6.927831934108866 \\ \hline
 2Pet & 7.163029618166046 \\ \hline
 Heb & 7.386919153066945 \\ \hline
 1Tim & 7.770543696461224 \\ \hline
 2John & 7.943318349523352 \\ \hline
 Phlm & 8.329605437730203 \\ \hline
 Eph & 8.612294442945819 \\ \hline
 1Thess & 8.899858487169308 \\ \hline
 Matt & 9.693678966679508 \\ \hline
 Acts & 9.700489665529872 \\ \hline
 Titus & 9.804481544422595 \\ \hline
 Jude & 10.03478412469002 \\ \hline
 2Thess & 10.379014777612305 \\ \hline
 John & 10.404714409545871 \\ \hline
 1Pet & 10.552026086581963 \\ \hline
 Luke & 11.148630974497753 \\ \hline
 Col & 11.244820523085805 \\ \hline
 Mark & 12.224830001939202 \\ \hline
 1John & 13.041947903321775 \\ \hline
 3John & 13.333865818090239 \\ \hline
 Rev & 19.824662106823926 \\ \hline 
\end{longtable}


Eph
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Col & 2.3609806708099352 \\ \hline
 Phil & 4.074692422709013 \\ \hline
 2Tim & 5.1576756379507955 \\ \hline
 2Thess & 5.32091262046331 \\ \hline
 Jude & 6.429519356344312 \\ \hline
 2Pet & 7.094787445303593 \\ \hline
 Rom & 7.797311634922189 \\ \hline
 Acts & 7.847942989942897 \\ \hline
 1Thess & 7.932384582943782 \\ \hline
 2John & 8.25250664675242 \\ \hline
 2Cor & 8.437749735109865 \\ \hline
 Gal & 8.612294442945819 \\ \hline
 1Cor & 8.619380545971659 \\ \hline
 Titus & 8.652917841104854 \\ \hline
 1Pet & 8.685381698472085 \\ \hline
 Heb & 9.032483682085626 \\ \hline
 1Tim & 9.098224706866691 \\ \hline
 Jas & 9.517516729155506 \\ \hline
 Phlm & 9.904483746355698 \\ \hline
 Matt & 10.432615562269314 \\ \hline
 1John & 11.093272998064585 \\ \hline
 Luke & 11.197209346847472 \\ \hline
 3John & 11.387942654416358 \\ \hline
 Mark & 11.478587930258778 \\ \hline
 John & 13.492052186245019 \\ \hline
 Rev & 14.632467106599286 \\ \hline 
\end{longtable}


Phil
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
2Thess & 3.743576074890499 \\ \hline
 Eph & 4.074692422709013 \\ \hline
 2Tim & 4.080985743135747 \\ \hline
 2Cor & 4.507446899462842 \\ \hline
 1Thess & 5.187291306780544 \\ \hline
 Jude & 5.3529973370136865 \\ \hline
 Col & 5.739007455473995 \\ \hline
 Phlm & 6.212910605262698 \\ \hline
 Rom & 6.559658832524622 \\ \hline
 1Cor & 6.8095621465672505 \\ \hline
 Gal & 6.927831934108866 \\ \hline
 2Pet & 6.976244901588798 \\ \hline
 1Pet & 7.362437600257963 \\ \hline
 Titus & 8.625706983866053 \\ \hline
 Heb & 8.996867241213454 \\ \hline
 Acts & 9.061621886988657 \\ \hline
 Jas & 9.559517594566442 \\ \hline
 3John & 9.879233855901957 \\ \hline
 1Tim & 10.056139192073712 \\ \hline
 2John & 10.34884582024838 \\ \hline
 1John & 10.959145595487586 \\ \hline
 Luke & 12.728676716661727 \\ \hline
 Matt & 12.982965547698754 \\ \hline
 John & 13.49163960435913 \\ \hline
 Mark & 14.217385143550265 \\ \hline
 Rev & 18.02813071464653 \\ \hline 
\end{longtable}


Col
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Eph & 2.3609806708099352 \\ \hline
 2Thess & 5.468475270981354 \\ \hline
 Phil & 5.739007455473995 \\ \hline
 2Tim & 7.198377447288609 \\ \hline
 Jude & 8.550672535950751 \\ \hline
 Titus & 8.753522659821979 \\ \hline
 2Pet & 8.861531020872318 \\ \hline
 2John & 9.03950380212461 \\ \hline
 1Pet & 9.779128098094167 \\ \hline
 1Thess & 9.83325767733729 \\ \hline
 Rom & 9.98144735009302 \\ \hline
 2Cor & 10.172539684962665 \\ \hline
 Acts & 10.418140064290256 \\ \hline
 1Cor & 10.43528571770649 \\ \hline
 Phlm & 10.883532588172633 \\ \hline
 Heb & 10.943680002361875 \\ \hline
 1Tim & 10.980561680292086 \\ \hline
 Gal & 11.244820523085805 \\ \hline
 Jas & 11.474849252405225 \\ \hline
 1John & 11.770717308863905 \\ \hline
 Matt & 12.526479987093426 \\ \hline
 Luke & 13.670925587289256 \\ \hline
 3John & 13.73372401856001 \\ \hline
 Mark & 14.342928234537267 \\ \hline
 Rev & 15.213140460105995 \\ \hline
 John & 15.799653009352925 \\ \hline 
\end{longtable}


1Thess
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
2Thess & 2.9432926622927016 \\ \hline
 2Cor & 3.5831709969695367 \\ \hline
 Phil & 5.187291306780544 \\ \hline
 Rom & 5.562672736939286 \\ \hline
 2Tim & 6.1053473627754 \\ \hline
 2John & 6.732221577764145 \\ \hline
 Jas & 7.754277794253226 \\ \hline
 3John & 7.826868985385091 \\ \hline
 1Cor & 7.895460709124209 \\ \hline
 Eph & 7.932384582943782 \\ \hline
 2Pet & 8.493948313235821 \\ \hline
 Jude & 8.636760589021716 \\ \hline
 Gal & 8.899858487169308 \\ \hline
 Heb & 9.06111904251555 \\ \hline
 Phlm & 9.212284950091842 \\ \hline
 Acts & 9.789277095129279 \\ \hline
 1Pet & 9.801746744189156 \\ \hline
 Col & 9.83325767733729 \\ \hline
 Titus & 11.013048909349884 \\ \hline
 1John & 11.757880225841074 \\ \hline
 1Tim & 12.788256579171469 \\ \hline
 Matt & 13.166040445500222 \\ \hline
 Luke & 13.204306172337871 \\ \hline
 John & 13.71369308283147 \\ \hline
 Mark & 14.585334331558329 \\ \hline
 Rev & 17.2606162680904 \\ \hline 
\end{longtable}


2Thess
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
1Thess & 2.9432926622927016 \\ \hline
 Phil & 3.743576074890499 \\ \hline
 2Tim & 4.3939890439105405 \\ \hline
 Eph & 5.32091262046331 \\ \hline
 Col & 5.468475270981354 \\ \hline
 2Cor & 5.750838561889809 \\ \hline
 Jude & 6.482519630870105 \\ \hline
 Rom & 6.597659163278408 \\ \hline
 2John & 7.080979993815129 \\ \hline
 Titus & 7.208837011402443 \\ \hline
 Jas & 7.430148101067357 \\ \hline
 1Pet & 7.609416839352782 \\ \hline
 Phlm & 7.690568180297394 \\ \hline
 3John & 8.322927419278681 \\ \hline
 Heb & 8.33268287101203 \\ \hline
 2Pet & 8.477922793882962 \\ \hline
 Acts & 8.711506654093402 \\ \hline
 1Cor & 8.761443809163133 \\ \hline
 1John & 9.31977990060063 \\ \hline
 1Tim & 10.134941214578092 \\ \hline
 Gal & 10.379014777612305 \\ \hline
 Matt & 12.009534851244338 \\ \hline
 Luke & 12.04492799547027 \\ \hline
 John & 12.46014091223983 \\ \hline
 Mark & 13.55507990735967 \\ \hline
 Rev & 17.769507232903926 \\ \hline 
\end{longtable}


1Tim
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Titus & 4.317441163201198 \\ \hline
 2Tim & 6.445178946323636 \\ \hline
 Jas & 7.680119535701941 \\ \hline
 Gal & 7.770543696461224 \\ \hline
 Heb & 7.78076490539881 \\ \hline
 1Cor & 8.283817030355692 \\ \hline
 Rom & 8.444144360376796 \\ \hline
 Eph & 9.098224706866691 \\ \hline
 2Cor & 9.53777224016234 \\ \hline
 Jude & 9.620437615505121 \\ \hline
 2John & 9.68241725096013 \\ \hline
 Phil & 10.056139192073712 \\ \hline
 2Pet & 10.075827813779586 \\ \hline
 2Thess & 10.134941214578092 \\ \hline
 1Pet & 10.350272295366853 \\ \hline
 Acts & 10.567553742690878 \\ \hline
 Col & 10.980561680292086 \\ \hline
 Phlm & 11.440024142005205 \\ \hline
 1Thess & 12.788256579171469 \\ \hline
 Luke & 13.302681404703307 \\ \hline
 3John & 14.593689402632535 \\ \hline
 Mark & 14.731344772719343 \\ \hline
 1John & 14.774390912321072 \\ \hline
 John & 14.946319353391026 \\ \hline
 Matt & 15.001133513719347 \\ \hline
 Rev & 19.502434620726405 \\ \hline 
\end{longtable}


2Tim
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Phil & 4.080985743135747 \\ \hline
 Jude & 4.108539867238225 \\ \hline
 2Pet & 4.179558098638855 \\ \hline
 2Thess & 4.3939890439105405 \\ \hline
 2Cor & 4.72576351900792 \\ \hline
 Eph & 5.1576756379507955 \\ \hline
 Rom & 5.347651691181487 \\ \hline
 Acts & 5.528398577945508 \\ \hline
 1Cor & 5.599865151542004 \\ \hline
 Phlm & 5.63084202844056 \\ \hline
 1Thess & 6.1053473627754 \\ \hline
 Heb & 6.330060367286448 \\ \hline
 1Tim & 6.445178946323636 \\ \hline
 Gal & 6.785928983326744 \\ \hline
 Col & 7.198377447288609 \\ \hline
 2John & 7.611731874976947 \\ \hline
 Jas & 7.852435772385855 \\ \hline
 1Pet & 7.891086685830416 \\ \hline
 Titus & 8.1936759996299 \\ \hline
 3John & 8.322314089730803 \\ \hline
 Luke & 9.519565236668662 \\ \hline
 Matt & 9.785473187567574 \\ \hline
 1John & 10.901522953046426 \\ \hline
 Mark & 11.516673884347284 \\ \hline
 John & 12.148982543463408 \\ \hline
 Rev & 17.05793508686522 \\ \hline 
\end{longtable}


Titus
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
1Tim & 4.317441163201198 \\ \hline
 2Thess & 7.208837011402443 \\ \hline
 Jude & 7.31632222961266 \\ \hline
 2Tim & 8.1936759996299 \\ \hline
 1Cor & 8.199243241982249 \\ \hline
 Phil & 8.625706983866053 \\ \hline
 Eph & 8.652917841104854 \\ \hline
 Col & 8.753522659821979 \\ \hline
 2John & 9.586225223159214 \\ \hline
 Rom & 9.601923689084177 \\ \hline
 Gal & 9.804481544422595 \\ \hline
 2Cor & 10.640134011635926 \\ \hline
 1Thess & 11.013048909349884 \\ \hline
 Phlm & 11.217562020686868 \\ \hline
 Heb & 11.42775968242117 \\ \hline
 2Pet & 11.457095749268587 \\ \hline
 Jas & 11.647886495817415 \\ \hline
 3John & 12.400194926351592 \\ \hline
 1John & 12.63064240324077 \\ \hline
 Acts & 12.743731064008266 \\ \hline
 1Pet & 12.796446553015791 \\ \hline
 Luke & 12.83754770994 \\ \hline
 Mark & 14.109114845386244 \\ \hline
 Rev & 15.137645500505732 \\ \hline
 Matt & 15.37829088943846 \\ \hline
 John & 16.259662280026276 \\ \hline 
\end{longtable}


Phlm
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
3John & 4.857375518366468 \\ \hline
 2Tim & 5.63084202844056 \\ \hline
 Phil & 6.212910605262698 \\ \hline
 2John & 7.283312552750726 \\ \hline
 Jude & 7.465168215982802 \\ \hline
 2Pet & 7.643641327173146 \\ \hline
 2Thess & 7.690568180297394 \\ \hline
 2Cor & 8.268911865836756 \\ \hline
 Gal & 8.329605437730203 \\ \hline
 1Thess & 9.212284950091842 \\ \hline
 1Cor & 9.486700703180663 \\ \hline
 Rom & 9.771174850275099 \\ \hline
 Eph & 9.904483746355698 \\ \hline
 Col & 10.883532588172633 \\ \hline
 1Pet & 11.171906885552115 \\ \hline
 Titus & 11.217562020686868 \\ \hline
 1Tim & 11.440024142005205 \\ \hline
 John & 12.762588361337974 \\ \hline
 Acts & 13.471742486015694 \\ \hline
 Jas & 13.638259975930449 \\ \hline
 Heb & 14.025403014218568 \\ \hline
 1John & 14.272362925822446 \\ \hline
 Matt & 14.564184398991955 \\ \hline
 Luke & 14.904853202539176 \\ \hline
 Mark & 17.67813790680798 \\ \hline
 Rev & 21.254361996129752 \\ \hline 
\end{longtable}


Heb
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Rom & 3.589732464510037 \\ \hline
 2Pet & 5.175658371080429 \\ \hline
 Acts & 5.416026847796947 \\ \hline
 2Cor & 5.707156188036583 \\ \hline
 2Tim & 6.330060367286448 \\ \hline
 Jas & 6.406746235804077 \\ \hline
 Mark & 6.841319253495689 \\ \hline
 1Cor & 7.061425841167152 \\ \hline
 Gal & 7.386919153066945 \\ \hline
 1Tim & 7.78076490539881 \\ \hline
 Matt & 7.88402478953559 \\ \hline
 Luke & 8.067114764522275 \\ \hline
 1Pet & 8.193683070161079 \\ \hline
 2Thess & 8.33268287101203 \\ \hline
 Phil & 8.996867241213454 \\ \hline
 Eph & 9.032483682085626 \\ \hline
 1Thess & 9.06111904251555 \\ \hline
 Jude & 9.495033907696877 \\ \hline
 Col & 10.943680002361875 \\ \hline
 John & 11.210480742875674 \\ \hline
 Titus & 11.42775968242117 \\ \hline
 2John & 11.907777582390002 \\ \hline
 Rev & 12.46321011225798 \\ \hline
 1John & 13.263495422475312 \\ \hline
 3John & 13.696341786443817 \\ \hline
 Phlm & 14.025403014218568 \\ \hline 
\end{longtable}


Jas
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Rom & 3.9067570184953815 \\ \hline
 1Cor & 4.260601660084346 \\ \hline
 Matt & 4.4346324976013465 \\ \hline
 2John & 4.939340998530797 \\ \hline
 Luke & 5.291714777343677 \\ \hline
 2Cor & 5.860917943917871 \\ \hline
 Mark & 6.182932982948504 \\ \hline
 Heb & 6.406746235804077 \\ \hline
 Acts & 6.472835406060057 \\ \hline
 Gal & 6.597426691669961 \\ \hline
 2Pet & 6.850911851453528 \\ \hline
 Jude & 7.206992489404924 \\ \hline
 2Thess & 7.430148101067357 \\ \hline
 1Tim & 7.680119535701941 \\ \hline
 1Thess & 7.754277794253226 \\ \hline
 2Tim & 7.852435772385855 \\ \hline
 John & 8.721868817722687 \\ \hline
 Eph & 9.517516729155506 \\ \hline
 Phil & 9.559517594566442 \\ \hline
 1John & 9.876051832732749 \\ \hline
 1Pet & 10.062653568373358 \\ \hline
 3John & 10.227760232407563 \\ \hline
 Col & 11.474849252405225 \\ \hline
 Titus & 11.647886495817415 \\ \hline
 Rev & 11.797770304687862 \\ \hline
 Phlm & 13.638259975930449 \\ \hline 
\end{longtable}


1Pet
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
2Cor & 7.306147537348039 \\ \hline
 Phil & 7.362437600257963 \\ \hline
 2Thess & 7.609416839352782 \\ \hline
 Rom & 7.751629182606049 \\ \hline
 2Pet & 7.872029236949034 \\ \hline
 2Tim & 7.891086685830416 \\ \hline
 Heb & 8.193683070161079 \\ \hline
 Eph & 8.685381698472085 \\ \hline
 Jude & 9.145894534385286 \\ \hline
 Acts & 9.629174665717688 \\ \hline
 Col & 9.779128098094167 \\ \hline
 1Thess & 9.801746744189156 \\ \hline
 Jas & 10.062653568373358 \\ \hline
 1Tim & 10.350272295366853 \\ \hline
 Gal & 10.552026086581963 \\ \hline
 Luke & 10.589280497236954 \\ \hline
 1Cor & 10.801428149132054 \\ \hline
 Matt & 11.01860472708464 \\ \hline
 Phlm & 11.171906885552115 \\ \hline
 Mark & 11.240397808725703 \\ \hline
 3John & 12.342973677911544 \\ \hline
 Titus & 12.796446553015791 \\ \hline
 2John & 13.229612606404983 \\ \hline
 John & 13.477308495380738 \\ \hline
 Rev & 15.995224823702431 \\ \hline
 1John & 16.255018289712257 \\ \hline 
\end{longtable}


2Pet
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
2Tim & 4.179558098638855 \\ \hline
 Rom & 5.068264652963615 \\ \hline
 Acts & 5.082873396765076 \\ \hline
 Heb & 5.175658371080429 \\ \hline
 Jude & 5.671691541437243 \\ \hline
 1Cor & 6.236601819943239 \\ \hline
 2Cor & 6.368628606851557 \\ \hline
 Jas & 6.850911851453528 \\ \hline
 Phil & 6.976244901588798 \\ \hline
 Eph & 7.094787445303593 \\ \hline
 Gal & 7.163029618166046 \\ \hline
 Phlm & 7.643641327173146 \\ \hline
 3John & 7.7772514624107 \\ \hline
 1Pet & 7.872029236949034 \\ \hline
 2John & 8.10578725965267 \\ \hline
 2Thess & 8.477922793882962 \\ \hline
 1Thess & 8.493948313235821 \\ \hline
 Luke & 8.62071208429699 \\ \hline
 Col & 8.861531020872318 \\ \hline
 Matt & 9.082797677205104 \\ \hline
 1Tim & 10.075827813779586 \\ \hline
 Mark & 10.584373854975077 \\ \hline
 1John & 11.338415395563855 \\ \hline
 Titus & 11.457095749268587 \\ \hline
 John & 12.024894659343758 \\ \hline
 Rev & 17.79850209361776 \\ \hline 
\end{longtable}


1John
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
2John & 7.667529473755046 \\ \hline
 John & 8.411323797616504 \\ \hline
 2Thess & 9.31977990060063 \\ \hline
 Jas & 9.876051832732749 \\ \hline
 Rom & 10.30088385814545 \\ \hline
 Acts & 10.738945261034436 \\ \hline
 2Tim & 10.901522953046426 \\ \hline
 Phil & 10.959145595487586 \\ \hline
 1Cor & 10.964978350169366 \\ \hline
 Eph & 11.093272998064585 \\ \hline
 Luke & 11.17264101763682 \\ \hline
 2Pet & 11.338415395563855 \\ \hline
 Jude & 11.627188554800423 \\ \hline
 2Cor & 11.669816665478802 \\ \hline
 1Thess & 11.757880225841074 \\ \hline
 Col & 11.770717308863905 \\ \hline
 3John & 12.341030897943835 \\ \hline
 Titus & 12.63064240324077 \\ \hline
 Gal & 13.041947903321775 \\ \hline
 Heb & 13.263495422475312 \\ \hline
 Matt & 13.319468398025837 \\ \hline
 Mark & 13.325773953034545 \\ \hline
 Rev & 14.196820733475423 \\ \hline
 Phlm & 14.272362925822446 \\ \hline
 1Tim & 14.774390912321072 \\ \hline
 1Pet & 16.255018289712257 \\ \hline 
\end{longtable}


2John
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Jas & 4.939340998530797 \\ \hline
 3John & 4.973085154000499 \\ \hline
 1Thess & 6.732221577764145 \\ \hline
 Jude & 6.853020640291435 \\ \hline
 2Thess & 7.080979993815129 \\ \hline
 Phlm & 7.283312552750726 \\ \hline
 2Tim & 7.611731874976947 \\ \hline
 1John & 7.667529473755046 \\ \hline
 Gal & 7.943318349523352 \\ \hline
 2Cor & 7.9806914148624415 \\ \hline
 2Pet & 8.10578725965267 \\ \hline
 Eph & 8.25250664675242 \\ \hline
 John & 8.609675216567437 \\ \hline
 Rom & 8.643309820482035 \\ \hline
 Col & 9.03950380212461 \\ \hline
 1Cor & 9.057562497589577 \\ \hline
 Rev & 9.517225302237614 \\ \hline
 Titus & 9.586225223159214 \\ \hline
 1Tim & 9.68241725096013 \\ \hline
 Phil & 10.34884582024838 \\ \hline
 Luke & 10.996672989658158 \\ \hline
 Matt & 11.411612200679972 \\ \hline
 Acts & 11.486116236413995 \\ \hline
 Mark & 11.563196454726096 \\ \hline
 Heb & 11.907777582390002 \\ \hline
 1Pet & 13.229612606404983 \\ \hline 
\end{longtable}


3John
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Phlm & 4.857375518366468 \\ \hline
 2John & 4.973085154000499 \\ \hline
 Jude & 5.64052290300648 \\ \hline
 2Pet & 7.7772514624107 \\ \hline
 1Thess & 7.826868985385091 \\ \hline
 2Tim & 8.322314089730803 \\ \hline
 2Thess & 8.322927419278681 \\ \hline
 Phil & 9.879233855901957 \\ \hline
 Jas & 10.227760232407563 \\ \hline
 John & 10.265949844393411 \\ \hline
 Eph & 11.387942654416358 \\ \hline
 1John & 12.341030897943835 \\ \hline
 1Pet & 12.342973677911544 \\ \hline
 Titus & 12.400194926351592 \\ \hline
 Gal & 13.333865818090239 \\ \hline
 Rom & 13.368059306084888 \\ \hline
 Mark & 13.581649263068126 \\ \hline
 2Cor & 13.617121499640714 \\ \hline
 Heb & 13.696341786443817 \\ \hline
 Col & 13.73372401856001 \\ \hline
 Rev & 14.124352261904734 \\ \hline
 1Tim & 14.593689402632535 \\ \hline
 Acts & 16.380265256484805 \\ \hline
 1Cor & 16.707154203096355 \\ \hline
 Luke & 18.053114680370125 \\ \hline
 Matt & 19.944348788153366 \\ \hline 
\end{longtable}


Jude
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
2Tim & 4.108539867238225 \\ \hline
 Acts & 4.916097429993837 \\ \hline
 Phil & 5.3529973370136865 \\ \hline
 3John & 5.64052290300648 \\ \hline
 2Pet & 5.671691541437243 \\ \hline
 Eph & 6.429519356344312 \\ \hline
 Luke & 6.473497387400187 \\ \hline
 2Thess & 6.482519630870105 \\ \hline
 2John & 6.853020640291435 \\ \hline
 Matt & 6.961803874406476 \\ \hline
 1Cor & 7.0657256993816775 \\ \hline
 Jas & 7.206992489404924 \\ \hline
 Titus & 7.31632222961266 \\ \hline
 Phlm & 7.465168215982802 \\ \hline
 Col & 8.550672535950751 \\ \hline
 1Thess & 8.636760589021716 \\ \hline
 Rom & 8.81927986491159 \\ \hline
 1Pet & 9.145894534385286 \\ \hline
 2Cor & 9.317805067829227 \\ \hline
 Heb & 9.495033907696877 \\ \hline
 1Tim & 9.620437615505121 \\ \hline
 Gal & 10.03478412469002 \\ \hline
 Mark & 10.453955571142572 \\ \hline
 John & 11.469453846497478 \\ \hline
 1John & 11.627188554800423 \\ \hline
 Rev & 16.437010253461374 \\ \hline 
\end{longtable}


Rev
\begin{longtable}{|c|c|}
\hline
 Book & $a$-value \\ \hline
Mark & 9.052949729869212 \\ \hline
 2John & 9.517225302237614 \\ \hline
 Matt & 10.503923386527115 \\ \hline
 Acts & 11.117753366041498 \\ \hline
 Luke & 11.15379430845007 \\ \hline
 Jas & 11.797770304687862 \\ \hline
 Heb & 12.46321011225798 \\ \hline
 John & 12.775960411976842 \\ \hline
 3John & 14.124352261904734 \\ \hline
 1John & 14.196820733475423 \\ \hline
 Eph & 14.632467106599286 \\ \hline
 Titus & 15.137645500505732 \\ \hline
 Col & 15.213140460105995 \\ \hline
 Rom & 15.409420118108146 \\ \hline
 1Pet & 15.995224823702431 \\ \hline
 Jude & 16.437010253461374 \\ \hline
 2Tim & 17.05793508686522 \\ \hline
 1Thess & 17.2606162680904 \\ \hline
 1Cor & 17.659429830249145 \\ \hline
 2Thess & 17.769507232903926 \\ \hline
 2Pet & 17.79850209361776 \\ \hline
 Phil & 18.02813071464653 \\ \hline
 2Cor & 18.032964178582887 \\ \hline
 1Tim & 19.502434620726405 \\ \hline
 Gal & 19.824662106823926 \\ \hline
 Phlm & 21.254361996129752 \\ \hline 
\end{longtable}



\newpage
\section{Code}
The reader.py file reads the csv file and creates an array for each book (contained in a dictionary) that contains all the words (by Strong's number) in sequential order.
\lstinputlisting[language=Python]{reader.py}

\newpage

The nt.py file uses the result of the reader.py file.  There are a couple useful functions (descriptions in the code): freqCount, freqCountTwenty (used to create Appendix A), freqDict, compare1, mostSimilarTo, printToTextFile (used to create Appendix B), printToDict, and mostSimilarIn.  The final output is the result of the table in the section 4. 
\lstinputlisting[language=Python]{nt.py}


\end{document}